\section{Introduction}
This project is about the simulation of a piece of cloth interacting with rigid bodies.\par

During the simulation, the cloth interacts with its environment i.e. self-collision and cloth-object collision must be regarded. We use collision detection between the cloth object represented as mass spring system and rigid body objects represented as triangle mesh. Self-collision of the cloth object is not considered.\par

The collision response method uses spring penalty forces for the mass points of the cloth object. The rigid objects do not respond to collisions. The equation of motion for the mass spring system is solved by a symplectic euler method.\par

The appearance of the cloth is primarily the response to these conditions. The simulation shows the cloth falling down and covering a sphere object. We use OpenGL to render the scene.

\section{Installation}
\subsection{Minimal Requirements}
\begin{itemize}
	\item Linux based OS
	\item Memory min. 4\,MB RAM
	\item CPU min. speed 1\,GHz with 2 cores e.g. i5-2540 or better
	\item approx 1\,MB free hard-disk space
\end{itemize}
\subsection{Dependencies}
\begin{itemize}
	\item OpenGL and utility libraries (package libglu***-dev e.g. libglu-mesa-dev; depends on graphics hardware)
	\item OpenGL utilities toolkit (package freeglut3-dev)
	\item libPNG  -- PNG file handling (package libpng12-dev)
	\item Eigen -- math utilities for vector and matrix arithmetics (package libeigen3-dev)
	\item C++ compiler with C++ 11 support e.g. GNU GCC g++ V4.7 or better
\end{itemize}
\subsection{Compiling}
Go to the sub-folder \it{build} of the project folder and run \tt{make all}.\par
If you want to compile directly on the console use the following options:  
\begin{itemize}
	\item -std=c++11 or -std=c++0x (use the C++ 11 dialect)  
	\item -lGL (the OpenGL library)  
	\item -lGLU (OpenGL utility library)
	\item -lglut (the GL utility Toolkit - make sure 'freeglut' is installed, some extensions not present in the GLUT API are used)  
	\item -lpthread (or -lthread; manage threads)  
	\item -lpng (library to handle PNG files)
\end{itemize}
